\documentclass{letter}
\usepackage{hyperref,color}

%%%%%%%%%% Start TeXmacs macros
\usepackage[german]{babel}
\newcommand{\emdash}{---}
\newcommand{\tmem}[1]{{\em #1\/}}
\newcommand{\tmtextbf}[1]{{\bfseries{#1}}}
\newcommand{\tmtextit}[1]{{\itshape{#1}}}
\newcommand{\tmtextsf}[1]{{\sffamily{#1}}}
\newenvironment{itemizedot}{\begin{itemize} \renewcommand{\labelitemi}{$\bullet$}\renewcommand{\labelitemii}{$\bullet$}\renewcommand{\labelitemiii}{$\bullet$}\renewcommand{\labelitemiv}{$\bullet$}}{\end{itemize}}
\definecolor{grey}{rgb}{0.75,0.75,0.75}
\definecolor{orange}{rgb}{1.0,0.5,0.5}
\definecolor{brown}{rgb}{0.5,0.25,0.0}
\definecolor{pink}{rgb}{1.0,0.5,0.5}
%%%%%%%%%% End TeXmacs macros

\begin{document}

{\small \tmtextsf{\tmtextbf{{\large \begin{center}
  Academic Experience
\end{center}}}



{\noindent}\begin{tabular}{l}
  \hline
  \quad
\end{tabular}

\subsubsection*{Project Management}

\begin{itemizedot}
  \item DFG Forschungsstipendium BE 2501/6-1 {\tmem{ONTOLEO -- Higher-Order
  Ontology-Reasoning with LEO-II}}. (2009-2010).
  
  \item EU FP7 IIF grant PIIF-GA-2008-219982 {\tmem{THFTPTP {\emdash} An
  Infrastructure for Typed Higher-order Form Automated Theorem Proving}}
  (2008-2009).
  
  \item Scientific {\small Coordinator of the European Union Research Training
  Network CALCULEMUS {\emdash} \tmtextit{Systems for integrated Computation
  and Deduction} funded in the EU 5th Framework (2000-2004).}
  
  \item {\small Project leader and principal investigator of the OMEGA group
  with approximately 10 researchers at Saarland University.}
  
  \item Principal investigator of the project DIALOG in the Collaborative
  Research Center \tmtextit{Resource-adaptive Cognitive Processes} (SFB 378)
  at Saarland University:
  \begin{itemizedot}
    \item 2005-2008: Natural language-based Interaction with a Mathematical
    Assistant System
    
    \item 2001-2004: Tutorial Dialog with a Mathematical Assistant System 
  \end{itemizedot}
  \item Principal investigator of the project OMEGA in the Collaborative
  Research Center \tmtextit{Resource-adaptive Cognitive Processes} (SFB 378)
  at Saarland University:
  \begin{itemizedot}
    \item 2005-2008: Agent-oriented Proof Planning
    
    \item 2001-2004: Resource-adaptive Proof Planning
  \end{itemizedot}
  \item {\small Head of the Saarland node of the European Union research
  network \tmtextit{Mathematical Knowledge Management (MKM) (until 2004)}.}
  
  \item {\small Researcher in the \ projects HOTEL: \tmtextit{Higher-Order
  Theorem Proving with Equality} and FABEON: \tmtextit{Flexible Adaptive Proof
  Presentation} funded by the DFG (until 2003).}
\end{itemizedot}
{\noindent}\begin{tabular}{l}
  \hline
  \quad
\end{tabular}

\subsubsection*{Trustee, Editorial Boards, and Committees}

\begin{itemize}
  \item Executive officer of the The International Federation for
  Computational Logic (IFCOLOG).
  
  \item Editorial board member of the Logic Journal of the IGPL, Elsevier.
  
  \item Trustee of the Conference on Automated Deduction (CADE), elected in
  2008.
  
  \item Editorial board member of the Journal of Algorithms in Cognition,
  Informatics and Logic, Elsevier.
  
  \item Steering committee member of the User Interfaces for Theorem Provers
  (UITP) workshop series.
  
  \item Editorial board member of the Journal of Applied Logic, Elsevier.
  
  \item {\small IJCAR steering committee member in 2004 representing the
  CALCULEMUS community.}
  
  \item CALCULEMUS Trustee (2004-2006, ex-officio).
  
  \item Member of the Collaborative Research Center "Resource-adaptive
  Cognitive Processes" (SFB378) at Saarland University.
\end{itemize}
{\noindent}\begin{tabular}{l}
  \hline
  \quad
\end{tabular}

\subsubsection*{Conference and Workshop Chair}

\begin{itemize}
  \item IJCAR'08 Workshop: \href{http://www.cs.miami.edu/\~{
  }geoff/Conferences/ESHOL/}{Evaluation of Systems for \ Higher-Order Logic
  (ESHOL'08)}, Sydney, Asutralia, August . 2008.
  
  \item TPHOLs'08 Workshop: \href{http://www.ags.uni-sb.de/\~{
  }omega/workshops/UITP08/}{User Interfaces for Theorem Provers (UITP'08)},
  Montreal, Canada, August 2008.
  
  \item Workshop Chair of \href{http://www.cs.miami.edu/\~{
  }geoff/Conferences/CADE//Archive/CADE-21/}{The 21nd Conference on Automated
  Deduction (CADE-21)}, Bremen, Germany, July 2007.
  
  \item LPAR'06 Workshop: \href{http://www.cs.miami.edu/\~{
  }geoff/Conferences/IWIL-6/}{The 6th International Workshop on the
  Implementation or Logics (IWIL'06)}, Phnom Penh, Cambodia, November, 2006.
  
  \item IJCAR'06 Workshop:
  \href{http://www.easychair.org/FLoC-06/UITP.html}{User Interfaces for
  Theorem Provers (UITP'06)}, Seattle, USA, August 2006.
  
  \item \href{http://www.ags.uni-sb.de/\~{
  }omega/workshops/MathDIALOG06/}{MathDIALOG-06}: An informal Workshop on
  Tutorial Natural Language DIALOG in Mathematics, \ Saarbr\"ucken, March
  2006.
  
  \item LPAR'05 Workshop: \href{../ESHOL-05/website.html}{Empirically
  Successful Automated Higher-Order Reasoning (ESHOL'05)}, Montego Bay,
  Jamaica, December 2005.
  
  \item \href{http://www.ags.uni-sb.de/\~{
  }omega/workshops/TheoremaOmega05/}{THEOREMA-ULTRA-OMEGA-Workshop},
  Saarbr\"ucken, November 2005.
  
  \item \href{../HOL-HYL-WS-2005/website.html}{First Saarbr\"ucken-Nancy
  Workshop on Higher-Order Logics and Hybrid Logics}, Saarbr\"ucken, Germany,
  May 2005.
  
  \item IJCAR'04 Workshop on
  \href{http://www.risc.uni-linz.ac.at/conferences/IJCAR-WS7/}{Computer-Supported
  Mathematical Theory Development}, University College Cork, Cork, Ireland,
  2004.
  
  \item Joint {\small \href{http://www.ags.uni-sb.de/\~{
  }omega/workshops/Deduktionstreffen04/}{Annual Meeting }}of the German
  Interest Groups on Deduction Systems and on Logics in Computer Science,
  {\small Saarbr\"ucken, Germany, October 2004.}
  
  \item {\small \href{http://www.eurice.de/calculemus/autumn-school/}{EU
  CALCULEMUS Autumn School}, Pisa, Italy, September/October 2002.}
  
  \item {\small \href{../ded00/}{Annual Meeting }of the German Interest Group
  on Deduction Systems, Saarbr\"ucken, Germany, October 2000.}
\end{itemize}
{\noindent}\begin{tabular}{l}
  \hline
  \quad
\end{tabular}

\subsubsection*{Organization of other Events}

\begin{itemize}
  \item Co-Organizer of
  \href{http://events.cs.bham.ac.uk/cicm08/doctoral/}{Doctoral Programme} at
  CICM'08 (Collocation of AISC'08, Calculemus'08, MKM'08)
  
  \item Organizer and Chair of the CALCULEMUS Session at the Workshop:
  {\color{black} {\small \href{http://www.win.tue.nl/dw/monet}{Mathematics on
  the Semantic Web}}}{\small , Eindhoven, Netherlands, 2003.}
  
  \item Organizer and Chair of the {\small
  \href{file:///home/chris/www/events/mtr-meeting/mtr-meeting.html}{EU Midterm
  Review Meeting} of the CALCULEMUS Research Training Network, Saarbr\"ucken,
  Germany, 2003.}
\end{itemize}
{\noindent}\begin{tabular}{l}
  \hline
  \quad
\end{tabular}

\subsubsection*{Member in Program Committees}

\begin{itemize}
  \item \href{}{PxTP 2011}: The Workshop on Proof eXchange for Theorem
  Proving, Wroclaw, Poland, August 1, 2011.
  
  \item \href{http://cicm11.cs.unibo.it/cicm11/}{CICM 2011}: Conference on
  Intelligent Computer Mathematics, Bertinoro, Forli (ITALY), July 18-23,
  2011.
  
  \item \href{http://www.icaart.org/}{ICAART 2011}: 3rd International
  Conference on Agents and Artificial Intelligence, Rome, Italy, January
  28-30, 2011.
  
  \item \href{http://www.informatik.uni-bremen.de/\~{
  }autexier/mips2010/}{MIPS 2010}: Workshop on Mathematically Intelligent
  Proof Search, Paris, France, July 10, 2010.
  
  \item \href{http://uitp10.cs.unibo.it/}{UITP 2010}: 9th International
  Workshop on User Interfaces for Theorem Provers, {\small Edinburgh,
  Scotland, July 20, \ 2010.}
  
  \item \href{http://clc.cs.uiowa.edu/EMSQMS/}{EMS+QMS 2010}: International
  Workshop on Evaluation Methods for Solvers and Quality Metrics for
  Solutions, Edinburgh, UK, July 20, 2010.
  
  \item \href{http://www.informatik.uni-bremen.de/\~{
  }autexier/aisc2010/}{AISC-2010}: 10th International Conference on Artificial
  Intelligence and Symbolic Computation, Paris, France, July (5-10), 2010.
  
  \item \href{http://www.floc-conference.org}{IJCAR-2010}: 5th International
  Joint Conference on Automated Reasoning{\small , Edinburgh, Scotland, July
  (16-19) 2010.}
  
  \item \href{http://www.wcc2010.org/SEC2010/}{IFIP SEC-2010}: 25th IFIP
  International Information Security Conference, Brisbane, Australia,
  September (20-23), 2010.
  
  \item \href{http://www.iasted.org/CONFERENCES/ipc-674.html}{AIA 2010}: The
  Tenth IASTED International Conference on Artificial Intelligence and
  Applications, Innsbruck, Austria, February (15-17), 2010.
  
  \item \href{http://tphols.in.tum.de/}{TPHOLs'09}: The 22nd International
  Conference on Theorem Proving in Higher Order Logics (TPHOLs 2009), Munich,
  Germany, August (17-20), 2009
  
  \item \href{http://heim.ifi.uio.no/martingi/Tableaux09/}{Tableaux'09}: The
  17th International Conference on Automated Reasoning with Analytic Tableaux
  and Related Methods, Oslo, Norway, July (7-10), 2009
  
  \item \href{http://www.csc.liv.ac.uk/\~{ }konev/iwil2008/}{IWIL'08}: \ The
  7th International Workshop on the Implementation of Logics, Doha, Qatar,
  November (23-27), 2008
  
  \item \href{http://www.cs.ualberta.ca/\~{ }piotr/KEAPPA08/}{KEAPPA'08}: The
  LPAR 2008 Workshop on Knowledge Exchange: Automated Provers and Proof
  Assistants, Doha, Qatar, November (23-27), 2008
  
  \item
  \href{http://www.eprover.org/EVENTS/PAAR-2008/paar-2008.html}{PAAR'08}:
  IJCAR '08 Workshop on Practical Aspects of Automated Reasoning, Sydney,
  Australia, August (10-11), 2008.
  
  \item \href{http://www.cs.miami.edu/\~{ }tptp/CASC/J4/}{CASC'08}:
  (Competition Panel Member) The ATP System Competition at the 4th
  International Joint Conference on Automated Reasoning, Sydney, Australia,
  August (10-15), 2008.
  
  \item \href{http://events.cs.bham.ac.uk/cicm08/aisc08/}{AISC'08}: 9th
  International Conference on Artificial Intelligence and Symbolic
  Computation, {\small Birmingham, England, }July/August, 2008.
  
  \item
  \href{http://events.cs.bham.ac.uk/cicm08/calculemus08/}{CALCULEMUS'08}: 16th
  Symposium on the Integration of Symbolic Computation and Mechanized
  Reasoning{\small , Birmingham, England, }July/August, 2008.
  
  \item \href{http://www.ijcar.org/2008/}{IJCAR'08}: 4th International Joint
  Conference on Automated Reasoning{\small , Sydney, Australia, August
  (10-15), 2008.}
  
  \item \href{http://www.cs.miami.edu/\~{ }tptp/CASC/21/}{CASC'07:}
  (Competition Panel Member) The CADE ATP System Competition at the 21st
  International Conference on Automated Deduction Bremen, Germany, July
  (17-20), 2007.
  
  \item \href{http://www.cadeconference.org/meetings/cade21}{CADE'07}: The
  21nd Conference on Automated Deduction (CADE-21), Bremen, Germany, July
  (17-20), 2007.
  
  \item \href{http://www.ki2007.uos.de/}{KI'07}: 30th Annual German Conference
  on Artificial Intelligence, Osnabr\"uck, Germany, September (10-12), 2007.
  
  \item \href{}{CALCULEMUS'07}: 15th Symposium on the Integration of Symbolic
  Computation and Mechanized Reasoning{\small , Linz, Austria, }June (27-30),
  2007.
  
  \item \href{http://www.cs.bham.ac.uk/\~{
  }mmk/events/deduktionstreffen07/}{Deduktionstreffen'07}: Annual Meeting of
  the German Interest Group on Deduction Systems, Koblenz, Germany, March
  (27/28), 2007.
  
  \item \href{http://www.lix.polytechnique.fr/\~{
  }hermann/LPAR2006/}{LPAR'06}: 12th International Conference on Logic for
  Programming Artificial Intelligence and Reasoning, \ \ Phnom Penh, Cambodia,
  November, 2006.
  
  \item \href{http://calculemus2006.loria.fr/}{CALCULEMUS'06}: 14th Symposium
  on the Integration of Symbolic Computation and Mechanized Reasoning{\small ,
  Genova, Italy, }July, 2006.
  
  \item \href{http://www.cs.miami.edu/\~{
  }geoff/Conferences/LARARL/}{LARARL'06}: The
  \href{http://logic.pdmi.ras.ru/\~{ }csr2006/}{CSR-2006} Workshop on Logic
  for Automated Reasoning and Automated Reasoning for Logic (LARARL),
  St.Petersburg, Russia, June, 2006.
  
  \item \href{http://www.cs.man.ac.uk/\~{ }ipratt/ICoS-5/}{ICoS'06}: 5th
  workshop on Inference in Computational Semantics, Manchester, UK, April,
  2006.
  
  \item \href{http://www.lpar.net/2005/}{LPAR'05}: 12th International
  Conference on Logic for Programming Artificial Intelligence and Reasoning,
  Montego Bay, Jamaica, December, 2005.
  
  \item \href{http://www.mkm-ig.org/meetings/mkm05/}{MKM'05}: 4th
  International Conference on Mathematical Knowledge Management, Bremen,
  Germany, July 2005.
  
  \item \href{http://4c.ucc.ie/ijcar/}{IJCAR'03}: 2nd International Joint
  Conference on Automated Reasoning{\small , Cork, Ireland, July, 2004.}
  
  \item {\small \href{http://www.cs.bham.ac.uk/\~{
  }vxs/ijcai03/}{IJCAI'03-WS}: Workshop on Agents and Automated Reasoning,
  Acapulco, Mexico, August, 2003.}
  
  \item \href{http://www-calfor.lip6.fr/\~{ }rr/Calculemus03/}{CALCULEMUS'03}:
  11th Symposium on the Integration of \ Symbolic Computation and Mechanized
  Reasoning{\small , Rome, Italy, September, 2003.}
  
  \item \href{http://floc02.diku.dk/CADE/}{CADE'02}: Conference on Automated
  Deduction{\small  in Copenhagen, Denmark, July, 2002.}
  
  \item \href{http://www.ags.uni-sb.de/\~{ }calculemus2002/}{CALCULEMUS'02}:
  10th Symposium on the Integration of \ Symbolic Computation and Mechanized
  Reasoning{\small , Marseilles, France, July, 2002.}
  
  \item {\small \href{http://www.cs.bham.ac.uk/\~{
  }mmk/events/ijcar01-future/}{IJCAR'01-WS:} Workshop on Future Directions in
  Automated Reasoning -- Problems and Ideas for a new Millennium in Siena,
  Italy, June, 2001.}
\end{itemize}
{\noindent}\begin{tabular}{l}
  \hline
  \quad
\end{tabular}

\subsubsection*{Further Reviewing}

\begin{itemize}
  \item LMCS: Logical Methods in Computer Science, 2010
  
  \item AI Communications: 2009
  
  \item DIGITEO: Recherche en sciences \& technologies de l'information,
  France, 2009
  
  \item AMAI: Annals of Mathematics and Artificial Intelligence, 2008
  
  \item MCS: Mathematics in Computer Science, 2008
  
  \item ISSAC: International Symposium on Symbolic and Algebraic Computation,
  2008
  
  \item DIGITEO: Recherche en sciences \& technologies de l'information,
  France, 2009
  
  \item NSERC: Natural Sciences and Engineering Research Council of Canada,
  2008
  
  \item ACM TOCL: Transactions on Computational Logic, 2007, 2008
  
  \item LMS: LMS Journal of Computation and Mathematics, 2004, 2005
  
  \item {\small JAR: Journal of Automated Reasoning, 2002, 2005}, 2006, 2008,
  2009
  
  \item JSC: {\small Journal of Symbolic Computation}, 2000, 2001
  
  \item CSL: Conference on Computer Science and Logic, 2007, 2009
  
  \item CADE: {\small Conference on Automated Deduction}, 1996, 2002, 2005
  
  \item LICS: {\small IEEE Symposium on Logic in Computer Science}, 2000, 2001
  
  \item ECAI: {\small {\color{black} European Conference on Artificial
  Intelligence}}, 2000, 2002
  
  \item {\small KI: German Conference on Artificial Intelligence}, 2001
  
  \item JELIA: {\small European Conference on Logics in Artificial
  Intelligence}, 2000
  
  \item FLAIRS: International FLAIRS Conference, 2000
  
  \item CL: International Conference on Computational Logic, 2000
  
  \item CALCULEMUS: {\small Symposium on the Integration of \ Symbolic
  Computation and Mechanized Reasoning, 2001, 2002, 2003}
  
  \item LPAR: {\small International Conference on Logic for Programming
  Artificial Intelligence and Reasoning}, 2002
  
  \item {\small Various International Workshops}
\end{itemize}
{\noindent}\begin{tabular}{l}
  \hline
  \quad
\end{tabular}

\subsubsection*{Fund Raising Activities}

\begin{itemize}
  \item 2009-2010: DFG Forschungsstipendium BE 2501/6-1 ONTOLEO --
  Higher-Order Ontology-Reasoning with LEO-II
  
  \item 2007: DFG Grant Proposal {\tmem{Automated Intelligent Tutoring of
  Mathematical Proofs}}. (not funded)
  
  \item 2007: EU FP7 IIF grant (PIIF-GA-2008-219982).{\tmem{THFTPTP -- An
  Infrastructure for Typed Higher-order Form Automated Theorem Proving}} (\~{
  }130.000 Euro)
  
  \item 2006/2007: EPSRC Research grant (EP/D070511/1) {\tmem{LEO II: An
  Effective Higher-Order Theorem Prover}} with Larry Paulson at Computer
  Laboratory, University of Cambridge, UK. (92,512 Pounds)
  
  \item {\small 2005-2008: DFG Grant in the Collaborative Research Centre 378
  on \tmtextit{Resource-adaptive Cognitive Processes}, Project MI 4
  OMEGA:}\tmtextit{{\small  Agent-oriented Proof Planning}} (\~{ }500.000
  Euro)
  
  \item {\small 2005-2008: DFG Grant in the Collaborative Research Centre
  378\tmtextit{ on Resource-adaptive Cognitive Processes}, Project MI 3
  DIALOG: \tmtextit{Natural Language-based Interaction with a Mathematics
  Assistance System}} (\~{ }450.000 Euro)
  
  \item 2004-2007: DAAD Research Exchange Grant (ARC) with Edinburgh/Prof.
  Kamareddine \ (\~{ }7.000 Euro)
  
  \item Coordinator of renewal proposal for the European Union Research
  Training Network CALCULEMUS-II \tmtextit{Computer-supported Mathematical
  Knowledge Evolution} in the EU 6th Framework. (not funded)
  
  \item {\small 2002: EU IST-Grant for CALCULEMUS Autumn School} (\~{ }20.000
  Euro)
  
  \item {\small 2002: 25 European Union Comenius grants for high school
  teachers to attend the CALCULEMUS Autumn School in Pisa} \ (\~{ }30.000
  Euro)
  
  \item {\small 2002: Research server and NFS server for the OMEGA group at
  Saarland University} \ (\~{ }30.000 Euro)
  
  \item {\small 2001-2004: DFG grant in the Collaborative Research Centre 378
  on \tmtextit{Resource-adaptive Cognitive Processes}, Project MI 4
  OMEGA:}\tmtextit{{\small  Resource-Adaptive Proof Planning}} (\~{ }420.000
  Euro)
  
  \item {\small 2001-2004: DFG grant in the Collaborative Research Centre
  378\tmtextit{ on Resource-adaptive Cognitive Processes}, Project MI 3
  DIALOG: \tmtextit{Tutorial Dialogue with a Mathematics Assistance System}}
  (\~{ }400.000 Euro)
  
  \item 2000-2004: Scientific Cordinator of the EU research training network
  CALCULEMUS. (\~{ }1.500.000 Euro)
  
  \item 2000: EPSRC grant (GR/M99644) {\tmem{Agent-Oriented Theorem Proving}}
  with Manfred Kerber at the University of Birmingham (55.944 Pounds)
  
  \item {\small 2000 and before: Involved in the successful preparation and
  implementation of various individually funded research projects by \ the DFG
  (Germany), EU, and the EPSRC (UK).} Amongst them were DFG grant HOTEL on
  {\tmem{Higher-Order Automated Theorem Proving with Equality}} with J\"org
  Siekmann and Michael Kohlhase. 
\end{itemize}
{\noindent}\begin{tabular}{l}
  \hline
  \quad
\end{tabular}

\subsubsection*{Industry Contacts}

\begin{itemize}
  \item {\small In my role as coordinator of the \ CALCULEMUS research
  training network I have been involved in the initiation and implementation
  of several industry internships of CALCULEMUS young researchers at leading
  European companies.}
  
  \item Articulate Software, Napa Valley, USA
\end{itemize}
{\noindent}\begin{tabular}{l}
  \hline
  \quad
\end{tabular}

\subsubsection*{Membership in Organizations}

\begin{itemizedot}
  \item GI, Gesellschaft f\"ur Informatik
  
  \item Deutscher Hochschulverband
  
  \item Association for Automated Reasoning
  
  \item AAAI, American Association for Artificial Intelligence
\end{itemizedot}
{\noindent}\begin{tabular}{l}
  \hline
  \quad
\end{tabular}}}

\end{document}
